---
title: "Parameterized Reports using *purrr*"
author: "Robert C Cline Sr."
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc_float: true
    toc: true
params:
 team: 'Blazers'
 # data: openintro::nba_teams_19  
 # data:  file.csv
---  



```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)  
library(readr)
library(kableExtra)
library(openintro)
```

### Introduction  
This is a parameterized R Markdown document created in RMarkdown. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.  A parameterized report is created using the dataset *nba_players_19* from the R *openintro package*.    

This specific example of parameterized reports covers the NBA team members of the `r params$team` team.  

The dataset is split into groups by team using *group_split()* function from the R *dplyr package*. 

<br> 

### The `r params$team` NBA Team for the year 2019.    



 



```{r eval=FALSE}

## library(openintro)
nba <- nba_players_19  

teams <- nba %>% 
  group_by(team) %>% 
  group_split()  

head(teams[1]) %>% 
  
kbl(caption = "First group of Teams: head(teams[1])") %>% 
kable_classic(full_width = F, html_font = "Cambria", position = "left")  

``` 

A path is created to provide naming of the individual reports.  First, *nba_players_19 dataset* is subset to provide the unique name for the nba teams.  

There are `r nba_players_19 %>% nrow()` team members on `r nba_players_19 %>% distinct(team) %>% summarise(n())` NBA teams. 

The average NBA team has an average of `r round(nba_players_19 %>% summarize(nrow(nba_players_19)/n_distinct(team)),1)` players. 

The total number of team members on the `r params$team` team is  **`r nba_players_19 %>% filter(team == params$team) %>% count(team) %>% select(-team)` players**.  


```{r eval=FALSE}
nba_players_19 %>% 
  distinct(team) %>% 
  summarise(n())
```

```{r}
nba_players_19 %>% 
  summarize(nrow(nba_players_19)/n_distinct(team))
```


```{r count_team_members}
## library(openintro)
nba <- openintro::nba_players_19  

nba %>% 
  filter(team == params$team) %>% 
  count(team) %>% 
  select(-team)
```




```{r team-members-table}
library(gt)
nba %>% 
  filter(team == params$team) %>% 
  gt() %>% 
  tab_header(
    title = "Team Members for the year 2019" #,
#    subtitle = md("`r params$team`")
  )

```

```{r}
teamnames <- unique(nba$team)
# paste0(teams, ".csv")

# filesout  to output folder
filesout <- here("output", paste0(teamnames, ".html") )

head(filesout)
```

The *map2()* function is called from the *purrr package* 

```{r}
### Modifying Tracts for Params Output

nba_teams <- nba %>%
  dplyr::filter(team==params$team) 
```


```{r}
gt::gt(nba_teams)
```


```{r results='hide', eval=FALSE}
library(here)
library(rmarkdown)
fs::dir_create(here("output"))
map2(teams, filesout, write_csv)

map2(teams, filesout, render)
```

```{r eval=FALSE}
library(fs)
library(here)
fs::file_delete(here("output", "."))
```

